REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-11-29 main.tex
up to 5.2.2

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$. This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations. Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equillibrium chemistry \citet[e.x.][]{Hu2016}.

@@

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equillibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8} \mbox{ M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc. This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012} (need more cite). We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.

@@

In both panels, we also include recent observational constraints from these relationships. We include the KS fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits 
%mm
   and errors 
from \citet{Roychowdhury2014} (blue), and the individual points 
%mm
   (black squares) 
from the recent SHIELD sample \citep{Teich2016}; we include only the fit and 1$\sigma$ errors from \citep{Shi2011} for the ESL (black), which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}. In both relationships our simulations fit well around the median observed fit, spanning the 1 $\sigma$ variations about the mean.

@@

The molecular gas content of low mass dwarf galaxies like this is generally considered to be small, (references). Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas fractions anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values. Given As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ typically of 0.17 - 0.20, in between this range, but significantly above the few percent often found in models. This means ignoring the $H_2$ component of our galaxies leads to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL. This does not lead to a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for low mass, low metallicity dwarf galaxies. However, our non-equillibrium chemical model for $H_2$ formation and destruction is relatively simple, and does not account for C and O chemistry, a detailed dust model, or cosmic rays; all of which may significantly affect $f_{\rm H_2}$. Simulations in \citet{Hu2016} and \citet{Hu2017}, which contain a more detailed non-equillibrium chemistry model than included here, give very low $f_{\rm H_2}$, below $10^{-4}$ for their full feedback simulations; even their simulations without any radiation feedback only reach $f_{\rm H_2} \sim 2 \times 10^{-3}$. However, their simulated dwarf galaxies are more massive ($M_{\rm vir} = 10^{10} M_{\odot}$) and higher metallicity ($Z = 0.1 Z_{\odot}$) than those examined here. This disagreement warrants additional investigation, particularly as making predictions for the H$_2$ content of low mass dwarf galaxies is valuable. We do note that there is some possible observational evidence for higher than expected ($\sim 15$ \%) molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.

@@

We note that this cooling curve shows only an approximation of the local cooling and heating rates used in the simulations for two reasons. First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal line cooling and heating rates are used. The actual primordial heating and cooling rates are calculated self-consistently using the non-equillibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}. However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations. Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from LW dissociation, and ionization heating. We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables. 
%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.

>>>>

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$. This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations. Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.

@@

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8} \mbox{ M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc. This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012} (need more cite). We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.

@@

In both panels, we also include recent observational constraints from these relationships. For the KS relationship we include the fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits 
%mm
   and errors 
from \citet{Roychowdhury2014} (blue), and the individual points 
%mm
   (black squares) 
from the recent SHIELD sample \citep{Teich2016}, while for the ESL relationship we include only the fit and 1$\sigma$ errors (black) from \citet{Shi2011}, which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}. In both relationships our simulations fit well around the median observed fit, spanning the 1 $\sigma$ variations about the mean.

@@

The molecular gas content of low mass dwarf galaxies like this is generally considered 
to be small (references). Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas fractions anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values. As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.17--0.20, within this range, but significantly exceeding the few percent often found in models. This means ignoring the H$_2$ component of our galaxies leads to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL. This does not lead to a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for low mass, low metallicity dwarf galaxies. However, 
%mm
    we do not fully resolve the turbulent density perturbations in which 
    H$_2$ forms most efficiently \citep{Glover2007}, and
our non-equilibrium chemical model for H$_2$ formation and destruction is relatively simple: it does not account for C and O chemistry, a detailed dust model, or cosmic rays, all of which may significantly affect $f_{\rm H_2}$.

Simulations by \citet{Hu2016} and \citet{Hu2017}, which contain a more detailed non-equilibrium chemistry model than included here, give very low $f_{\rm H_2}$, below $10^{-4}$ for their full feedback simulations; even their simulations without any radiation feedback only reach $f_{\rm H_2} \sim 2 \times 10^{-3}$. However, their simulated dwarf galaxies are more massive ($M_{\rm vir} = 10^{10} M_{\odot}$) and higher metallicity ($Z = 0.1 Z_{\odot}$) than those examined here. This disagreement warrants additional investigation, particularly as making predictions for the H$_2$ content of low mass dwarf galaxies is valuable. We do note that there is some possible observational evidence for higher than expected ($\sim 15$ \%) molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.

@@

We note that this cooling curve shows only an approximation of the local cooling and heating rates used in the simulations for two reasons. First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal line cooling and heating rates are used. The actual primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}. However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations. Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from LW dissociation, and ionization heating. We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables. 
%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.
